Revisiting the Relationship between Short-Chain Fatty Acids, the Microbiota, and Colorectal Tumors

### 2018-07-23 submission/supplemental.Rmd
add supplemental tables of correlations and sig diffs

>>>>

**Table S5: Spearman tests between OTU relative abundance and SCFA concentrations.**

\scriptsize

```{r supplemental_table5, echo=FALSE, message=FALSE, warning=FALSE}

table_s5 <- read_csv("../data/process/tables/significant_reg_otu_comp_summary.csv") %>% 
  left_join(read_tsv("../data/process/final.taxonomy") %>% 
              select(-Size) %>% 
  mutate(Taxonomy = str_replace_all(Taxonomy, "\\(\\d*\\)", "")) %>% 
  separate(Taxonomy, c("kingdom", "phyla", "class", "order", "family", "genus", "species"), sep = ";") %>% 
              select(OTU, family), by = c("otu" = "OTU")) %>% 
  select(otu, family, genus, dx, scfa, estimate, p.value, bh) %>% 
  mutate_at(vars(p.value:bh), function(x) format(x, scientific = T, digits = 3)) %>% 
  mutate(estimate = round(estimate, digits = 3), 
         family = str_replace_all(family, "_unclassified", ""), 
         family = str_replace_all(family, "_", " "), 
         genus = str_replace_all(family, "_unclassified", ""), 
         genus = str_replace_all(family, "_", " "))

colnames(table_s5) <-  c("OTU", "Family", "Genus", "Group", "SCFA", "Rho", "P-value", "BH")

kable(table_s5, format = "markdown", align = 'c', padding = 2)

\normalsize

**Table S6: Wilcoxson tests between OTU relative abundance and high or low SCFA concentrations based on the overall median.**

\scriptsize

```{r supplemental_table6, echo=FALSE, message=FALSE, warning=FALSE}

table_s6 <- read_csv("../data/process/tables/significant_class_otu_comp_summary.csv") %>% 
  left_join(read_tsv("../data/process/final.taxonomy") %>% 
              select(-Size) %>% 
  mutate(Taxonomy = str_replace_all(Taxonomy, "\\(\\d*\\)", "")) %>% 
  separate(Taxonomy, c("kingdom", "phyla", "class", "order", "family", "genus", "species"), sep = ";") %>% 
              select(OTU, family), by = c("otu" = "OTU")) %>% 
  select(otu, family, genus, dx, scfa, p.value, bh) %>% 
  mutate_at(vars(p.value:bh), function(x) format(x, scientific = T, digits = 3)) %>% 
  mutate(family = str_replace_all(family, "_unclassified", ""), 
         family = str_replace_all(family, "_", " "), 
         genus = str_replace_all(family, "_unclassified", ""), 
         genus = str_replace_all(family, "_", " "))

colnames(table_s6) <-  c("OTU", "Family", "Genus", "Group", "SCFA", "P-value", "BH")

kable(table_s6, format = "markdown", align = 'c', padding = 2)

\normalsize
